Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
expand todo
rewrite the topology remark. Also fix some spaces in leanline

\todo[inline]{\leanline{∀ j : J, α j} or \leanline{(j : J) -> α j} ?}

@@

    \item \sloppy In \leanline{Lean}, we have the \leanline{class
      PseudoEMetricSpace (α : Type u) extends EDist}, where
      \leanline{EDist} comes with an extended distance

@@

      stands for $[0, \infty]$), and the extension to
      \leanline{PseudoEMetricSpace} consists of the components,
      \leanline{edist_self}, \leanline{edist_comm},
      \leanline{edist_triangle} providing the properties of the
      pseudo-metric, and \leanline{toUniformSpace},
      \leanline{uniformity_edist} defining a uniform space from the
      extended pseudo-metric. Such a space does not come with a

@@

    \item \sloppy For topological spaces, we have \leanline{class
      TopologicalSpace(α : Type u) : Type u}, which comes with
      \leanline{IsOpen : Prop}, \leanline{isOpen_univ : IsOpen
        Set.univ}, \leanline{isOpen_inter} and

@@

    \item Any (extended pseudo-)metric on $\alpha$ defines a topology,
      namely the topology generated by $\mathcal H := \{\{y:
      r(x,y)<\varepsilon\}: x \in \alpha, \varepsilon \in
      (0,\infty)\}$. Actually, in \leanline{mathlib}, as we have seen
      above, every extended pseudo-metric defines a uniform space, and
      a uniform space is a \leanline{class UniformSpace(α : Type u)
        extends TopologicalSpace , UniformSpace.Core} (where the
      uniformity is defined in \leanline{UniformSpace.Core}), which
      connects the \leanline{uniformity} with the topology using
      \leanline{∀ (s : Set α), IsOpen s ↔ ∀ (x : α), x ∈ s → {p | p.fst = x → p.snd ∈ s} ∈ uniformity}. In particular, a
      uniform space defines a topological space, which can be used by
      the typeclass system.

@@

%The next result talks about an \leanline{induced_outer_measure} in
%terms of {\tt mathlib}.
The next result extends a set function on a semi-ring to an outer measure.

>>>>

\todo[inline]{\leanline{∀ j : J, α j} or \leanline{(j : J) -> α j} ? Explain somewhere that this is the mathlib notation for the product space}

@@

    \item \sloppy \leanline{mathlib} provides the \leanline{class PseudoEMetricSpace (α : Type u)},
      which comes with an extended pseudo-distance

@@

      stands for $[0, \infty]$), and the properties
      \leanline{edist_self} (distance to self is zero),
      \leanline{edist_comm} (commutativity) and
      \leanline{edist_triangle} (triangle inequality).
      That class also comes with \leanline{toUniformSpace} and
      \leanline{uniformity_edist}, defining a uniform space from the
      extended pseudo-metric.
    \item A uniform space (\leanline{class UniformSpace (α : Type u)}) does not come with a

@@

    \item \sloppy A topological spaces is defined in \leanline{mathlib} as \leanline{class TopologicalSpace(α : Type u)},
      which comes with a predicate \leanline{IsOpen}, and properties \leanline{isOpen_univ : IsOpen Set.univ}, \leanline{isOpen_inter} and

@@

      An uniform spaces defines a topology, given by
      \leanline{∀ (s : Set α), IsOpen s ↔ ∀ (x : α), x ∈ s → {p | p.fst = x → p.snd ∈ s} ∈ uniformity}.
%    \item Any (extended pseudo-)metric on $\alpha$ defines a topology,
%      namely the topology generated by $\mathcal H := \{\{y:
%      r(x,y)<\varepsilon\}: x \in \alpha, \varepsilon \in
%      (0,\infty)\}$. Actually, in \leanline{mathlib}, as we have seen
%      above, every extended pseudo-metric defines a uniform space, and
%      a uniform space is a \leanline{class UniformSpace(α : Type u) extends TopologicalSpace, UniformSpace.Core} (where the
%      uniformity is defined in \leanline{UniformSpace.Core}), which
%      connects the \leanline{uniformity} with the topology using
%      \leanline{∀ (s : Set α), IsOpen s ↔ ∀ (x : α), x ∈ s → {p | p.fst = x → p.snd ∈ s} ∈ uniformity}. In particular, a
%      uniform space defines a topological space, which can be used by
%      the typeclass system.

@@

The next result extends a set function on a semi-ring to an outer measure.
